Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (Coleoptera: Curculionidae), with notes on their distribution and phylogeny

### 2018-05-07 tex/manuscript.tex
Nico edits

\title{Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Coleoptera: Curculionid{\ae}), with notes on their distribution and phylogeny}

@@

%\keywords{Biogeography, cladistics, concept taxonomy, desert, Entiminae, \textit{Minyomerus}, new species, provenance, weevils} - KEYWORDS PROVIDED DURING SUBMISSION.

\begin{abstract}
	This contribution adopts the taxonomic concept annotation and alignment approach. 
	Accordingly, and where indicated, previous and newly inferred meanings of taxonomic names are individuated according to one specific source.
	Articulations among these concepts and pairwise, logically consistent alignments of original and revisionary classifications are also provided, in addition to conventional nomenclatural provenance information. 
	Descriptions of four species belonging to the broad-nosed weevil genera \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Curculionidae [non-focal]: Entiminae [non-focal]: Tanymecini [non-focal]) are presented.
	Prior to this study, \textit{Minyomerus} sec. Jansen \& Franz, 2015 contained 17 species species distributed throughout the desert and plains regions of North America.
	We thoroughly describe these four species as new to science: \textit{M. ampullaceus} sec. Jansen \& Franz (2015) (henceforth: [JF2015]), sp. n., \textit{M. franko} [JF2015], sp. n., \textit{M. sculptilis} [JF2015], sp. n., and \textit{M. tylotos} [JF2015], sp. n. 
	A cladistic analysis using 52 morphological characters of 26 terminal taxa (5/21 outgroup/ingroup) yielded a single most-parsimonious cladogram (L = 99, CI = 60, RI = 80). 
	The analysis supports the monophyly of Minyomerus [JF2015] with eight unreversed synapomorphies, in corroboration of prior work.
	Accordingly, each of the four new species is placed within \textit{Minyomerus} [JF2015], and their species-group placement, possible biogeographic origins, and natural history are discussed in detail.
\end{abstract}

@@

\section*{Introduction}\label{sec:intro}
	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2015] is currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionid{\ae} [non-focal]: Entimin{\ae} [non-focal] - higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}). 
	A recent phylogenetic revision of the genus recognized a total of 17 described species distributed throughout the desert and plains regions of North America \citep{jansen2015}.

	Members of the genus \textit{Minyomerus} [JF2015] are phytophagous, and may be found on a variety of host plants, especially the creosote bush (\textit{Larrea tridentata} (DC.) Coville [non-focal; Zygophyllaceae [non-focal]), broomweed (\textit{Gutierrezia lagasca} [non-focal; Asteraceae [non-focal), sagebrush (\textit{Artemisia} Linnaeus [non-focal]; Asteraceae [non-focal]), and occasionally on other various Asteraceae [non-focal] \citep{jansen2015}. 
	While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host feeding on the leaf tissue; all other life stages remain unknown.
	Species of this genus are commonly found in deserts throughout western North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts; however, their range extends throughout the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, M\'{e}xico \citep{obrien1982, jansen2015}. 
	The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.

	\textit{Minyomerus} [JF2015] belongs to the broad-nosed weevils, subfamily Entimin{\ae} [non-focal], on the basis of having a short, broad rostrum and dehiscent mandibular process \citep{marvaldi1997, anderson2002, oberprieler2007, oberprieler2014, marvaldi2014}.
	They are clothed in appressed, circular scales, generally in earth-tones from white to dark brown, with sub-recumbent to erect, interspersed setiform scales (`set{\ae}') arranged in rows on the elytral intervals, and can range in length from 2.8 to 6.0 mm \citep{jansen2015}.
	The genus has been classified in the tribe Tanymecini [non-focal] based on the presence of post-ocular vibriss{\ae} that project anteriorly from the anterior prothoracic margin, although the exact placement and sister taxa of this genus within the tribe are currently unknown \citep{howden1959, howden1970, howden1982, jansen2015}.

	The genus is diagnosed by a unique combination of synapomorphic traits, described by \citet{jansen2015}, and as follows:

	\begin{enumerate}[itemsep=-0.4em]
		\item The integument is covered by appressed scales that are sub-circular and overlap posteriorly.
		\item The nasal plate is present as a broad, scale-covered, chevron-shaped ridge demarcating the epistoma.
		\item A sulcus posteriad of nasal plate is present.
		\item The scrobe is sub-equal in length to the funicle and club combined.
		\item The head is directed slightly ventrally.
		\item The metatibial apex lacks setiform bristles yet displays bristles that are shorter to sub-equal in length to the surrounding set{\ae} and conical to lamelliform.
		\item The mesotarsi are slightly shorter than the mesotibi{\ae}.
		\item All tarsi lack pads of setiform set{\ae} but have stout, spiniform set{\ae}.
	\end{enumerate}

	The following additional characters are useful for identifying members of \textit{Minyomerus} [JF2015], especially when differentiating the former from other genera of Tanymecini [non-focal] that may be found together in the same desert habitats, viz. \textit{Isodrusus} Sharp, 1911 [non-focal], \textit{Isodacrys} Sharp, 1911 [non-focal], and \textit{Pandeleteinus} Champion, 1911 [non-focal] (see also \citealt{anderson2002}):

	\begin{enumerate} [itemsep=-0.4em]
		\item The intercoxal process of the prosternum is medially divided into two halves, with the procox{\ae} apparently contiguous in most.
		\item The elytral humeri are rounded rather than angled and protruding.
		\item The profemora are not dilated and lack spines.
		\item The protibi{\ae} are ventrally excavated by a longitudinal groove or concavity.
		\item A distinct scrobe is present and directed ventrad of the eye, with a more or less apparent tooth formed by an overhang of the dorsal margin.
	\end{enumerate}

	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet well circumscribed by the generic delimitation of the genus.
	As such, the addition of these new species \emph{does not} alter the definition of the genus (see \textbf{\nameref{sec:results}}), and we retain the taxonomic concept previously specified by \citet{jansen2015} when referring to this definition.
	For ease of legibility, especially when discussing differences in clade composition when comparing between this and previous work, we use the notation [JF2015] and [JF2018] to specify taxon concepts sec. Jansen \& Franz, 2015 and sec. Jansen \& Franz, 2018, respectively.
	Specifically, all clades inferred in this work will be designated according to the concept [JF2018], \emph{unless} there is perfect congruence (viz. synapomorphies and clade composition) with a clade previously resolved by \citet{jansen2015}, in which case the identifier [JF2015] will be retained.
	While this is the case for all of the previously described species, and a few select clades, we differentiate the newly inferred clade corresponding to the genus, and including the herein described species, as \textit{Minyomerus} [JF2018].

	Here we describe the four newly found species and provide images of the holotypes and of dissected genitalia for the purpose of identification.
	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus} [JF2015], based on the analysis provided in our previous work.
	An emended identification key to the species of \textit{Minyomerus} [JF2015] is given along with an updated checklist of the genus.
	Where possible, we make note of host-plant records and briefly consider the geographic distribution of the herein described species.
	A more extensive discussion of the habits, distribution, and delimitation of the genus (and all of its constituent species) can found in the generic revision \citep{jansen2015}.

\section*{Materials and Methods}\label{sec:methods} 
	In order to maximize the compatibility of the new species accounts with the higher-level generic account of \textit{Minyomerus} [JF2015], the methods used in this manuscript are aligned with those of \citet{jansen2015}.
	Here we provide an updated account of the procedures used to generate the species descriptions, distribution maps, and phylogeny herein.
	Most importantly, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.

	\subsection*{Acquisition of museum specimens}\label{ssec:museum} 
		The existing set of \textit{Minyomerus} [JF2015] specimens used in the revision of \citet{jansen2015} was supplemented with material from the following collections, using the codens of \citet{arnett1993}:

@@

			Georeferencing of localities was performed with Google Earth \citep{google2018} and reported in decimal degrees.
		Taxonomic names for associated host plants, as noted following each species account, are used in accordance with \citet{munz1973} and \citet{seinet2018}.

	\subsection*{Morphological analysis}\label{ssec:morph} 
		Our systematic and descriptive approach is complementary to \citet{jansen2015}, which in turn follows \citet{franz2010a, franz2010b, franz2012}.
		Terminology for exterior morphology is in general accordance with \citet{torre1989}.
		Additional morphological terms specific to (entimine [non-focal]) weevils were used as follows:
			\citet{ting1936} and \citet{morimoto2003} for mouthparts;
			\citet{thompson1992} for tibial apices and abdominal segments;
			and \citet{oberprieler2014} and \citet{howden1995} for male and female terminalia.

		Measurements were taken with a Leica M205 C stereomicroscope and associated software, Leica Application Suite (LAS), version 4.1.0.
		Overall body length and width were measured in dorsal view as the maximum distance between the rostral and elytral apices, and the maximum width of both elytra, respectively.
		Rostral length was measured in dorsal view as the distance between the epistomal apex and the anterior margin of the eyes.
		Rostral width was measured in dorsal view as the maximum distance between the dorsal margins of the rostrum near the point of antennal insertion.
		Pronotal length was measured in dorsal view as the length along the midline between the anterior and posterior margins.
		The width of an individual elytron was measured in dorsal view as the maximum distance between the lateral margin and the elytral suture.
		Other length and width measurements were also performed in dorsal orientation, using the maximum length and width of the corresponding structure (profemur, protibia, elytron, and {\ae}deagus).
		Images of mouthparts and terminalia were produced with the Leica microscope equipment, while habitus photographs were created with a Visionary Digital Passport II sytem using a Canon EOS Mark 5D II camera.

		Herein recognized species of \textit{Minyomerus} [JF2015] were delimited through application of the phylogenetic species concept \textit{sensu} \citet{wheeler2000}.
		Species descriptions are in alphabetical order, rather than phylogetic order, for ease of use.
		As in \citet{jansen2015}, the species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but excepting those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus} [JF2015].
		Likewise, descriptions of males emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
		The key to identifying species of \textit{Minyomerus} [JF2015] is arranged with emphasis being placed on the most readily observable diagnostic characters.
				This manuscript is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.

@@

		Although the tribe Tanymecini [non-focal] is cosmopolitan, the majority of New World species diversity in the tribe may be found in the subtribe Tanymecina [non-focal] \citep{alonso1999}.
		Thus, four of the five outgroup terminals are represented by species belonging to separate genera in the Tanymecina [non-focal]; viz. \textit{Isodacrys buchanani} Howden, 1961 [non-focal], \textit{Isodrusus debilis} Sharp, 1911 [non-focal], \textit{Pandeleteinus subcancer} Howden, 1969 [non-focal], and \textit{Pandeleteius cinereus} (Horn, 1876) [non-focal].
		Because generic relationships in the Tanymecini [non-focal] remain unresolved, we selected a relatively far-removed taxon to root the cladogram that would nevertheless display states applicable to the ingroup for characters under consideration \citep{rieppel2007, franz2014}.
		To this end we used the North American species \textit{Sitona californicus} (Fahr{\ae}us, 1840) [non-focal], of the tribe Sitonini Gistel, 1856 [non-focal].

@@

	\subsection*{Species distribution modeling}\label{ssec:dismo} 
		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2015] (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
		Cross-validation was used to leverage all available locality data; however, no models could be created for species with two or fewer documented localities.
		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim \citep{hijmans2005}.
		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of the genus.
		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling \citep{qgis2018}.

@@

			\textit{Minyomerus ampullaceus} is best differentiated from other congenerics by its unique body shape, which most prominently features a strongly constricted, sub-cylindrical pronotum and greatly protuberant elytra; this combination gives the species a distinctly flask- or bottle-shaped appearance.
			Due to the relatively poor condition of the scales and set{\ae} of the holotype, color and setation cannot be reliably used for identification.
			Fortunately, the elytra themselves are unique in shape, and diagnostic, together nearly 2\x the width of the pronotum at their widest point, and nearly 3/4\x as wide as long in dorsal view.

@@

				Set{\ae} recumbent to sub-recumbent, white to brown in color.

@@

				Partially covered with white, slightly opalescent scales, with 3 longer set{\ae}, and 1 shorter seta between these.

@@

				Rostrum in lateral view nearly square; apical margin broadly bisinuate and emarginate, with 2 pairs of large vibriss{\ae}. 

@@

			\paragraph{Antenn{\ae}}

@@

				Pronotum in lateral view with set{\ae} that reach beyond anterior margin by 1/2 of their length; these set{\ae} becoming evenly longer and more erect laterally, reaching a maximum length equal to 1/2 of length of eye. 
				Anterolateral margin with a reduced tuft of 6-7 post-ocular vibriss{\ae} present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibriss{\ae} sub-equal in length at 1/3 of anterior-posterior length of eye, except for three vibriss{\ae} achieving a maximum length similar to anterior-posterior length of eye.

@@

				Protibia/profemur length ratio 0.93; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding set{\ae}. 

@@

				Metatibial apex with almond shaped convexity ringed by 10 short, spiniform set{\ae}.

@@

				Posterior declivity angled at nearly 85\td to main body axis. Elytra with 10 complete stri{\ae}; stri{\ae} shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.

@@

			Named in reference to the shape of the body in dorsal view, which appears bottle-shaped due to the large elytra and comparatively cylindrical pronotum; ampullaceus = flasklike; Latin adjective \citep{brown1956}.

@@

			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829 [non-focal]; Cuculid{\ae} [non-focal]), the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).
			\textit{Minyomerus} species are only known to be phytophagous, not parasitic, phoretic, or necrophagous, so we believe that this specimen was most likely found in a nest, and was present there only incidentally because the nest was constructed in the host plant of this specimen \citep{jansen2015}.

@@

			\textit{Minyomerus franko} is readily distinguished from other congenerics by the strikingly long set{\ae} of the anterior margin of the pronotum, which project laterally up to 80\td from the longitudinal axis of the body and achieve a maximum length at least equaling the diameter of the eye.
			In addition, the set{\ae} lining the dorsal margin of the ocular impression are elongate and reach a length equal to 1/2 - 3/4\x the diameter of the eye.

@@

			The {\ae}deagus is relatively short and wide, and is abruptly constricted in the apical 1/5 of its length, thereafter tapered to a rounded point.

@@

				Set{\ae} linear to slightly apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, white or brown in color.

@@

				Covered with white scales, with 3 longer set{\ae}, and 1-2 shorter set{\ae} between these.
			\paragraph{Maxill{\ae}}

@@

region, set{\ae} covering 2/3 of dorsal surface area; dorsally with 7 apicomesal lacinial teeth; ventrally with 4 reduced lacinial teeth. 

@@

				I apically oblique, apical end forming a 45\td angle with base, with 2 apical set{\ae}; II sub-cylindrical, with 1 apical seta.

@@

				Set{\ae} sub-recumbent to sub-erect, white to brown in color.

>>>>

\title{Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (Coleoptera: Curculionidae), with notes on their distribution and phylogeny}

@@

%\keywords{Biogeography, cladistics, concept taxonomy, desert, Entiminae, \textit{Minyomerus}, new species, Region Connection Calculus, weevils} - KEYWORDS PROVIDED DURING SUBMISSION.

\begin{abstract}
	This contribution adopts the taxonomic concept approach, including the use of \textit{taxonomic concept labels} (name sec. [\textit{according to}] source) and Region Connection Calculus (RCC--5) articulations and alignments. 
	Prior to this study, the broad-nosed weevil genus \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Curculionidae [non-focal]: Entiminae [non-focal]: Tanymecini [non-focal]) contained 17 species distributed throughout the desert and plains regions of North America.
	In this revision of \textit{Minyomerus} sec. Jansen \& Franz, 2018, we describe the following four species as new to science: \textit{Minyomerus ampullaceus} sec. Jansen \& Franz, 2018 (henceforth: [JF2018]), \textbf{new species,} \textit{Minyomerus franko} [JF2018], \textbf{new species,} \textit{Minyomerus sculptilis} [JF2018], \textbf{new species,} and \textit{Minyomerus tylotos} [JF2018], \textbf{new species.}
	The four new species are added to, and integrated with, the preceding revision, and an updated key and phylogeny of \textit{Minyomerus} [JF2018] are presented. 
	A cladistic analysis using 52 morphological characters of 26 terminal taxa (5/21 outgroup/ingroup) yielded a single most-parsimonious cladogram (Length = 99 steps, Consistency Index = 60, Retention Index = 80). 
	The analysis reaffirms the monophyly of \textit{Minyomerus} [JF2018] with eight unreversed synapomorphies.
	The species-group placements, possible biogeographic origins, and natural history of the new species are discussed in detail.
\end{abstract}

@@

\section*{Introduction}\label{sec:intro}
	This phylogenetic revision follows \citet{jansen2015} in the use of the taxonomic concept approach; see \citet{fp2009, fea2016a, fea2016b}. Accordingly:

	\begin{enumerate}[itemsep=-0.4em]
		\item \textit{Taxonomic concept labels} -- i.e., the taxonomic name sec. (\textit{according to}) author or source (year) -- are used whenever we identify one specific usage of the taxonomic name. Examples: \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (henceforth: [JF2015]) and \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (henceforth: [JF2018]). We also employ this convention to express nomenclatural relationships. 
		\item Solely the taxonomic name -- without the sec. annotation -- is used to refer to the cumulative history (origin to present) of taxonomic concept labels in which that name participates. Example: \textit{Minyomerus} Horn, 1876.
		\item The annotation [non-focal] is added to taxonomic names whose meanings are not under scrutiny in the present context; such as names for higher-level weevil groups and associated plants (exempting common names). Example: Tanymecini Lacordaire, 1863 [non-focal].
	\end{enumerate}

	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2018] remains currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionidae [non-focal]: Entiminae [non-focal] -- higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}). 
	A recent phylogenetic revision of the \textit{Minyomerus} [JF2015] recognized a total of 17 described species, distributed throughout the desert and plains regions of North America \citep{jansen2015}.

	Members of the genus \textit{Minyomerus} [JF2018] are phytophagous, and may be found on a variety of host plants, especially the creosote bush \textit{Larrea tridentata} (DC) Coville [non-focal] (Zygophyllaceae [non-focal]), broomweed \textit{Gutierrezia} Lagasca [non-focal] (Asteraceae [non-focal]), sagebrush \textit{Artemisia} Linnaeus [non-focal] (Asteraceae [non-focal]), and occasionally on other various members of Asteraceae [non-focal] \citep{jansen2015}. 
	While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host, feeding on the leaf tissue. All other life stages remain unknown.
	Species of \textit{Minyomerus} [2018] are commonly found in deserts throughout western North America; including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts. However, their distributional range extends throughout the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, M\'{e}xico \citep{obrien1982, jansen2015}. 
	The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.

	\textit{Minyomerus} [JF2018] belongs to the broad-nosed weevils, subfamily Entiminae [non-focal], on the basis of having a short, broad rostrum and dehiscent mandibular process \citep{marvaldi1997, anderson2002, oberprieler2007, oberprieler2014, marvaldi2014}.
	The adults are clothed in appressed, circular scales, generally in earth-tones from white to dark brown, with sub-recumbent to erect, interspersed setiform scales ("setae") arranged in rows on the elytral intervals. Their length can range from 2.8 mm to 6.0 mm \citep{jansen2015}.
	The genus has been classified in the tribe Tanymecini [non-focal] based on the presence of post-ocular vibrissae that project anteriorly from the anterior prothoracic margin, although the exact placement and sister taxa of this genus within the tribe are currently unknown \citep{howden1959, howden1970, howden1982, jansen2015}.

	\textit{Minyomerus} [JF2015] was circumscribed by a unique combination of synapomorphic traits, described by \citet{jansen2015} as follows:

	\begin{enumerate}[itemsep=-0.4em]
		\item The integument is covered by appressed scales that are sub-circular and overlap posteriorly.
		\item The nasal plate is present as a broad, scale-covered, chevron-shaped ridge demarcating the epistoma.
		\item A sulcus posteriad of nasal plate is present.
		\item The scrobe is sub-equal in length to the funicle and club combined.
		\item The head is directed slightly ventrally.
		\item The metatibial apex lacks setiform bristles yet displays bristles that are shorter to sub-equal in length to the surrounding setae and conical to lamelliform.
		\item The mesotarsi are slightly shorter than the mesotibiae.
		\item All tarsi lack pads of setiform setae but have stout, spiniform setae.
	\end{enumerate}

	The following additional characters are useful for identifying members of \textit{Minyomerus} [JF2018], especially when differentiating the former from other genera of Tanymecini [non-focal] that may be found together in the same desert habitats; viz. \textit{Isodrusus} Sharp, 1911 [non-focal], \textit{Isodacrys} Sharp, 1911 [non-focal], and \textit{Pandeleteinus} Champion, 1911 [non-focal] (see also \citealt{anderson2002}):

	\begin{enumerate} [itemsep=-0.4em]
		\item Taehe intercoxal process of the prosternum is medially divided into two halves, with the procoxae apparently contiguous in most.
		\item The elytral humeri are rounded rather than angled and protruding.
		\item The profemora are not dilated and lack spines.
		\item The protibiae are ventrally excavated by a longitudinal groove or concavity.
		\item A distinct scrobe is present and directed ventrad of the eye, with a more or less apparent tooth formed by an overhang of the dorsal margin.
	\end{enumerate}

	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional, undescribed species. These are known to us only from limited numbers of specimens, yet are well circumscribed by -- i.e., intensionally included in \citep{fp2009} -- the recent generic delimitation of \textit{Minyomerus} [JF2015].
	In other words, the addition of these new species \emph{has not} required altering the intensional, property-based definition of the genus-level concept as circumscribed in \citet{jansen2015} (see \textbf{\nameref{sec:results}}). Our RCC--5 alignments (see \textbf{\nameref{sec:alignments}}) reflect this genus-level concept congruence while also showing which classificatory and phylogenetic structures have changed (Figs.~\ref{fig:align1}-\ref{fig:align3}).
	The precise use of the taxonomic concept labels in accordance with either [JF2015] or [JF2018] is meant to minimize the creation of new taxonomic concept labels (to counter label "inflation"; see \citet{fp2009}), while reflecting explicitly \emph{which} taxonomic concepts we consider as relevantly new and unique to the present study.

	Here we describe the four newly found species of \textit{Minyomerus} [JF2018] and provide images of the holotypes and of dissected genitalia for the purpose of identification.
	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus} [JF2018], based on the analysis provided in our previous work.
	An emended identification key to the species of \textit{Minyomerus} [JF2018] is given, along with an updated species checklist.
	Where possible, we make note of host-plant records, and briefly discuss the geographic distributions of the herein described species.
	A more extensive discussion of the habits, distribution, and delimitation of the \textit{Minyomerus} [JF2015] and all of its constituent species is provided in \citep{jansen2015}.

\section*{Materials and Methods}\label{sec:methods} 
	The methods used in this manuscript are generally consistent with \citet{jansen2015}. Relevant updates are detailed below. 
	In particular, we retain the format for the species descriptions, emphasizing only those characters that vary significantly from the generic circumscription of \textit{Minyomerus} [JF2015].

	\subsection*{Acquisition of museum specimens}\label{ssec:museum} 
		The set of specimens used in \citet{jansen2015} was supplemented with material from the following collections, using the codens of \citet{arnett1993}:

@@

			Georeferencing of localities was performed with Google Earth \citep{google2018}, following the WGS 84 standard, and reported in decimal degrees.
		Taxonomic names for associated host plants, as noted following each species account, are used in accordance with \citet{munz1973} and \citet{seinet2018}.

	\subsection*{Morphological analysis}\label{ssec:morph} 
		Our systematic and descriptive approach is complementary to \citet{jansen2015}, which in turn follows \citet{franz2010a, franz2010b, franz2012}.
		The terminology for exterior morphology is in general accordance with \citet{torre1989}.
		Additional morphological terms specific to (entimine [non-focal]) weevils were used as follows:
			\citet{ting1936} and \citet{morimoto2003} for mouthparts;
			\citet{thompson1992} for tibial apices and abdominal segments;
			and \citet{oberprieler2014} and \citet{howden1995} for male and female terminalia.

		Measurements were taken with a Leica M205 C stereomicroscope and associated software, Leica Application Suite (LAS), version 4.1.0.
		Overall body length and width were measured in dorsal view as the maximum distance between the rostral and elytral apices, and the maximum width of both elytra, respectively.
		Rostral length was measured in dorsal view as the distance between the epistomal apex and the anterior margin of the eyes.
		Rostral width was measured in dorsal view as the maximum distance between the dorsal margins of the rostrum near the point of antennal insertion.
		Pronotal length was measured in dorsal view as the length along the midline between the anterior and posterior margins.
		The width of an individual elytron was measured in dorsal view as the maximum distance between the lateral margin and the elytral suture.
		Other length and width measurements were also performed in dorsal orientation, using the maximum length and width of the corresponding structure (profemur, protibia, elytron, and aedeagus).
		Images of mouthparts and terminalia were produced with the Leica microscope equipment, while habitus photographs were created with a Visionary Digital Passport II system using a Canon EOS Mark 5D II camera.

		The herein newly recognized species of \textit{Minyomerus} [JF2018] were delimited through application of the phylogenetic species concept \textit{sensu} \citet{wheeler2000}.
		Species descriptions are in alphabetical order, rather than phylogenetic order, for ease of use.
		As in \citet{jansen2015}, the species descriptions represent unique, complementary accounts of the character states observed for each species, including their intra-specific variability, but excepting characters invariant within the genus-level concept of \textit{Minyomerus} [JF2015].
		Likewise, descriptions of males emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
		The key to identifying species of \textit{Minyomerus} [JF2018] is arranged with emphasis being placed on the most readily observable diagnostic characters.
		This manuscript is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic and RCC--5 alignment results.

@@

		Although the tribe Tanymecini [non-focal] is cosmopolitan, the majority of New World species diversity in the tribe may be found in the subtribe Tanymecina [non-focal] \citep{alonso1999}.
		Thus, four of the five outgroup terminals are represented by species belonging to separate genera in the Tanymecina [non-focal]; viz. \textit{Isodacrys buchanani} Howden, 1961 [non-focal], \textit{Isodrusus debilis} Sharp, 1911 [non-focal], \textit{Pandeleteinus subcancer} Howden, 1969 [non-focal], and \textit{Pandeleteius cinereus} (Horn, 1876) [non-focal].
		Because generic relationships in the Tanymecini [non-focal] remain unresolved, we selected a relatively far-removed taxon to root the cladogram that would nevertheless display states applicable to the ingroup for characters under consideration \citep{rieppel2007, franz2014}.
		To this end we used the North American species \textit{Sitona californicus} (Fahraeus, 1840) [non-focal], of the tribe Sitonini Gistel, 1856 [non-focal].

@@

	\subsection*{Taxonomic annotations and RCC--5}\label{ssec:taxanno} 
		In accordance with \citet{jansen2015}, we use the symbol "=" to indicate nomenclatural synonymy (objective/subjective); and the RCC--5 symbols \{$==$, $>$, $<$, $><$, !\} indicate taxonomic concept articulations. The annotations (INT) and (OST) indicate intensional and ostensive readings of articulations, and AND is used to connect multiple simultaneously recognized provenance relationships.
		Two \emph{intensional} alignments are produced as part of this revision, i.e., one that captures the non-/congruence of \textit{Minyomerus} [JF2018] versus \textit{Minyomerus} [JF2015] represented as rank-only classifications (Fig.~\ref{fig:align1}), and another that represents these as fully bifurcated phylogenies with newly assigned clade concept labels, shown in whole-concept resolution (Fig.~\ref{fig:align2}) and in split-concept resolution (Fig.~\ref{fig:align3}); see \citet{fea2018}.

		A detailed breakdown of our alignment approach and outcomes using an RCC--5 logic reasoner toolkit \citep{chen2014} is provided in the \textbf{Supplemental Information, SI1 to SI4}. For further information, see also \citet{jansen2015, fea2016a, fea2016b}.

	\subsection*{Species distribution modeling}\label{ssec:dismo} 
		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2018] (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
		Cross-validation was used to leverage all available locality data; however, no models could be created for species with two or fewer documented localities.
		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim \citep{hijmans2005}.
		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of the genus.
		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling \citep{qgis2018}.

@@

			\textit{Minyomerus ampullaceus} [JF2018] is best differentiated from other congenerics by its unique body shape, which most prominently features a strongly constricted, sub-cylindrical pronotum and greatly protuberant elytra; this combination gives the species a distinctly flask- or bottle-shaped appearance.
			Due to the relatively poor condition of the scales and setae of the holotype, color and setation cannot be reliably used for identification.
			However, the elytra themselves are unique in shape, and diagnostic, together nearly 2\x the width of the pronotum at their widest point, and nearly 3/4\x as wide as long in dorsal view.

@@

				Setae recumbent to sub-recumbent, white to brown in color.

@@

				Partially covered with white, slightly opalescent scales, with 3 longer setae, and 1 shorter seta between these.

@@

				Rostrum in lateral view nearly square; apical margin broadly bisinuate and emarginate, with 2 pairs of large vibrissae. 

@@

			\paragraph{Antennae}

@@

				Pronotum in lateral view with setae that reach beyond anterior margin by 1/2 of their length; these setae becoming evenly longer and more erect laterally, reaching a maximum length equal to 1/2 of length of eye. 
				Anterolateral margin with a reduced tuft of 6-7 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae sub-equal in length at 1/3 of anterior-posterior length of eye, except for three vibrissae achieving a maximum length similar to anterior-posterior length of eye.

@@

				Protibia/profemur length ratio 0.93; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding setae. 

@@

				Metatibial apex with almond shaped convexity ringed by 10 short, spiniform setae.

@@

				Posterior declivity angled at nearly 85\td to main body axis. Elytra with 10 complete striae; striae shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.

@@

			Named in reference to the shape of the body in dorsal view, which appears bottle-shaped due to the large elytra and comparatively cylindrical pronotum -- \textit{ampullaceus} = "flasklike"; Latin adjective \citep{brown1956}.

@@

			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [non-focal] (Cuculidae [non-focal]), the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).
			Species of \textit{Minyomerus} [JF2018] are only known to be phytophagous, not parasitic, phoretic, or necrophagous. Hence we believe that this specimen was most likely found in a nest, and was present there only incidentally because the nest was constructed in the host plant of this specimen \citep{jansen2015}.

@@

			\textit{Minyomerus franko} [JF2018] is readily distinguished from other congenerics by the strikingly long setae of the anterior margin of the pronotum, which project laterally up to 80\td from the longitudinal axis of the body and achieve a maximum length at least equaling the diameter of the eye.
			In addition, the setae lining the dorsal margin of the ocular impression are elongate and reach a length equal to 1/2 - 3/4\x the diameter of the eye.

@@

			The aedeagus is relatively short and wide, and is abruptly constricted in the apical 1/5 of its length, thereafter tapered to a rounded point.

@@

				Setae linear to slightly apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, white or brown in color.

@@

				Covered with white scales, with 3 longer setae, and 1-2 shorter setae between these.
			\paragraph{Maxillae}

@@

region, setae covering 2/3 of dorsal surface area; dorsally with 7 apicomesal lacinial teeth; ventrally with 4 reduced lacinial teeth. 

@@

				I apically oblique, apical end forming a 45\td angle with base, with 2 apical setae; II sub-cylindrical, with 1 apical seta.

@@

				Setae sub-recumbent to sub-erect, white to brown in color.
